\Title

### 2016-03-20 manuscript/manuscript.tex
Corrections to CRUST1 synthetic by Val

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Synthetic seismic data simulating point estimates of Moho depth.
        The point estimates were obtained by interpolating
        the Moho depth in (a).
    }
    \label{fig:crust1-data}
\end{figure*}

@@

The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
requires knowledge of the Moho depth at certain points
($\mathbf{z}_s^o$ in Eq.~\ref{eq:msehyper}),
usually from seismic experiments.
Thus, we must also generate synthetic seismic data about the Moho depth.
We produce such data by interpolating the Moho depth shown in
Fig.~\ref{fig:crust1-data}a on the same geographic coordinates
as the 937 points from the \citet{assumpcao2013a} data set.
The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.

@@

For the first cross-validation,
we separate the synthetic data (Fig.~\ref{fig:grid_separation}) into
a training set with twice the grid spacing of the original data
($N_{lat} \times N_{lon} = 80 \times 60$)
and a testing set with 14,121 observations.
We run the inversion for 16 different values of $\mu$
equally spaced in a logarithmic scale between $10^{-7}$ and $10^{-2}$.
For each of the 16 estimates we compute the MSE (Eq.~\ref{eq:msemu}),
shown in Fig.~\ref{fig:crust1-results}a as function of $\mu$.
The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
(indicated by the red triangle).

@@

Fig.~\ref{fig:crust1-results}c shows the final solution after both
cross-validation procedures.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:crust1-results}d shows the difference between
the true Moho depths (Fig.~\ref{fig:crust1-data}a)
and the estimated depths.
The maximum and minimum differences are, respectively,
9.8 and -8.2 km.
The largest absolute differences are located along the central and northern
Andes, where there is a sharp increase in the true Moho depth
(Fig.~\ref{fig:crust1-data}a).
Positive differences (indicating a too shallow estimate)
appear along the central portion of the Andes,
flanked by regions of negative differences (indicating a too deep estimate)
on the continental and Pacific sides.
Figs.~\ref{fig:crust1-results}e and g show the inversion residuals (difference
between the observed and predicted data).
The inversion residuals appear normally distributed,
with 0.03 mGal mean and a standard deviation of 4.10 mGal.
The residuals follow a similar, though reversed, pattern
to the differences shown in Fig.~\ref{fig:crust1-results}d.
The largest residuals (in absolute value) are along the Andes,
with the central portion being dominated by negative residuals
and flanked by positive residuals on both sides.
Figs.~\ref{fig:crust1-results}f and h show the differences between
the synthetic seismic data (Fig.~\ref{fig:crust1-data}c)
and the estimated Moho depths.
Once more, the largest differences are concentrated along the Andes,
particularly in the central Andes and near Ecuador and Colombia.
The differences are smaller along the Atlantic coast of South America,
with notable larger differences in a few points of northeastern Brazil
and along the Amazon river.
In general, large residuals are associated with sharp increases in Moho depth.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Simulated points where the Moho depths are known from seismological
        estimates (color dots).  Here, these point were obtained by
        interpolating the Moho depth in (a).
    }
    \label{fig:crust1-data}
\end{figure*}

@@

The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
requires knowledge of the Moho depth at certain points
($\mathbf{z}_s^o$ in Eq.~\ref{eq:msehyper}),
usually from seismic experiments.
Thus, we must also generate synthetic seismic data about the Moho depth.
We produce such data by interpolating the Moho depth shown in
Fig.~\ref{fig:crust1-data}a on the same 937 geographic coordinates
pinpointed in the data set of \citet{assumpcao2013a}.
The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.

@@

For the first cross-validation,
we separate the synthetic data (Fig.~\ref{fig:grid_separation}) into
a training set with twice the grid spacing of the original data
($N_{lat} \times N_{lon} = 80 \times 60$)
and a testing set with 14,121 observations.
We run the inversion for 16 different values of $\mu$
equally spaced in a logarithmic scale between $10^{-7}$ and $10^{-2}$.
For each of the 16 estimates we compute the MSE (Eq.~\ref{eq:msemu}),
shown in Fig.~\ref{fig:crust1-results}a as function of $\mu$.
The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
(red triangle in Fig.~\ref{fig:crust1-results}a).

@@

Fig.~\ref{fig:crust1-results}c shows the final solution after both
cross-validation procedures.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:crust1-results}d shows the difference between
the true Moho depths (Fig.~\ref{fig:crust1-data}a)
and the estimated depths (Fig.~\ref{fig:crust1-results}c).
The maximum and minimum differences are, respectively,
9.8 and -8.2 km.
The largest absolute differences are located along the central and northern
Andes, where there is a sharp increase in the true Moho depth
(Fig.~\ref{fig:crust1-data}a).
Positive differences (indicating a too shallow estimate)
appear along the central portion of the Andes,
flanked by regions of negative differences (indicating a too deep estimate)
on the continental and Pacific sides.
Figs.~\ref{fig:crust1-results}e and g show the gravity residuals,
defined as the difference between the observed and predicted gravity data.
The residuals appear normally distributed,
with 0.03 mGal mean and a standard deviation of 4.10 mGal.
The gravity residuals follow a similar, though reversed, pattern
to the differences shown in Fig.~\ref{fig:crust1-results}d.
The largest residuals (in absolute value) are along the Andes,
with the central portion being dominated by negative residuals
and flanked by positive residuals on both sides.
Figs.~\ref{fig:crust1-results}f and h show the differences between
the synthetic seismic data (Fig.~\ref{fig:crust1-data}c)
and the estimated Moho depths.
Once more, the largest differences are concentrated along the Andes,
particularly in the central Andes and near Ecuador and Colombia.
The differences are smaller along the Atlantic coast of South America,
with notable larger differences in a few points of northeastern Brazil
and along the Amazon river.
In general, large residuals are associated with sharp increases in Moho depth.
